The merger history of primordial-black-hole binaries inferred from GWTC-3

### 2022-09-29 latex/paper.tex
update

We denote the probability distribution function (PDF) of PBH masses by $P(m)$
which satisfies the following normalization condition
\e\label{norm}
    \int_{0}^{\infty} P(m)\, \rd m = 1.
\q 
Consequently the abundance of PBHs in the mass interval $(m, m+\rd m)$ is given 
by \cite{Chen:2018rzo}
\e 
    0.85 \fpbh\, P(m)\, \rd m,
\q 
where $\fpbh$ is the fraction of PBHs in CDM, and the coefficient $0.85$ is roughly the fraction of CDM in non-relativistic matter.
Similar to \cite{Liu:2019rnx}, one may define a quantity $\mpbh$ as
\e\label{mpbh}
    \frac{1}{\mpbh} = \int \frac{P(m)}{m} \rd m.
\q 
Furthermore, the present average number density of PBHs with mass $m$ in the 
present total average number density of PBHs, $F(m)$, can be obtained by
\cite{Liu:2019rnx}
\e\label{Fm} 
    F(m) = P(m) \frac{\mpbh}{m}.
\q

With the above definitions at hand, one can go directly to estimate the merger rate densities of PBH binaries contributed from different merger processes. We assume that PBHs are randomly distributed in the early Universe when they decouple from the cosmic background evolution \cite{Nakamura:1997sm,Sasaki:2016jop,Ali-Haimoud:2017rtz}. Due to gravitational interactions, two nearest PBHs would attract each other and form a bound system if they get the angular momentum from the torque of the third closest PBH. Because of gravitational radiations, PBH binaries would eventually merge and may be detected by \lvc. Let us consider the first-merger process now. Assuming PBHs posses a random distribution in the early Universe, the differential distribution, for three PBHs with masses $(m_i, m_i+dm_i)$, $(m_j, m_j+dm_j)$ and  $(m_l, m_l+dm_l)$, is given by \cite{Liu:2019rnx}

>>>>

The BBHs observed by LVK suggest that BHs should have a broad mass distribution, and hence we consider an extended mass function for PBHs. Here, we denote the probability distribution function (PDF) of PBH masses by $P(m)$ and demand the PDF to be normalized such that
\e\label{norm}
    \int_{0}^{\infty} P(m)\, \rd m = 1.
\q 
Assuming the fraction of PBHs in CDM is $\fpbh$, we can estimate the abundance of PBHs in the mass interval $(m, m+\rd m)$ as \citep{Chen:2018rzo}
\e 
    0.85 \fpbh\, P(m)\, \rd m,
\q 
where the coefficient $0.85$ is roughly the fraction of CDM in non-relativistic matter including both CDM and baryons. Following \cite{Liu:2019rnx}, we may also define the ``averaged" PBH mass, $\mpbh$, as
\e\label{mpbh}
    \frac{1}{\mpbh} = \int \frac{P(m)}{m} \rd m.
\q 
Then, we can obtain the average number density of PBHs with mass $m$ in the 
total number density of PBHs, $F(m)$, by \citep{Liu:2019rnx}
\e\label{Fm} 
    F(m) = P(m) \frac{\mpbh}{m}.
\q

We can now proceed to estimate the merger rate densities of PBH binaries by considering the merger history effect.

We assume that PBHs are randomly distributed in the early Universe when they decouple from the cosmic background evolution \cite{Nakamura:1997sm,Sasaki:2016jop,Ali-Haimoud:2017rtz}. Due to gravitational interactions, two nearest PBHs would attract each other and form a bound system if they get the angular momentum from the torque of the third closest PBH. Because of gravitational radiations, PBH binaries would eventually merge and may be detected by \lvc. Let us consider the first-merger process now. Assuming PBHs posses a random distribution in the early Universe, the differential distribution, for three PBHs with masses $(m_i, m_i+dm_i)$, $(m_j, m_j+dm_j)$ and  $(m_l, m_l+dm_l)$, is given by \cite{Liu:2019rnx}
